Self Regulation Ontology Retest Data: Initial Exploration

### 2017-03-07 SRO_Retest_Analyses.Rmd
made new notebook just looking at meaningful vars

for(i in 1:length(matching_dv_columns)){
  ttest_df[matching_dv_columns[i], 't_stat'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$statistic

  ttest_df[matching_dv_columns[i], 'p_val'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]])$p.value
}

@@

@@

>>>>

for(i in 1:length(matching_dv_columns)){
  ttest_df[matching_dv_columns[i], 't_stat'] <- pairwise.t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]], p.adjust.method = 'fdr')$statistic

  ttest_df[matching_dv_columns[i], 'p_val'] <- t.test(retest_subs_test_data[,matching_dv_columns[i]], rest_subs_test_data[,matching_dv_columns[i]], p.adjust.method = 'fdr')$p.value
}

@@

```{r eval=FALSE, echo=FALSE}
corrected_ttest <- function(df1, df2, col){

  x = df1[,col]
  y = df2[,col]

  n <- max(length(x), length(y))
  length(x) <- n                      
  length(y) <- n

  tmp = as.data.frame(cbind(x,y))

  tmp = tmp %>% 
    gather(key, value)

  return(pairwise.t.test(tmp$value,tmp$key, p.adjust.method = 'fdr'))
}
```

@@

- Ignore Pearson for now and just focus on Spearman
- Eventually want to get to interclass correlations (between versus within group variability - using anova)
- Clean everything on the whole sample and extract from that. Keep a record of everything that was transformed and whether it was normal at the end
